---
title: "Create example plots and tables"
output: rmarkdown::html_vignette
editor_options: 
  chunk_output_type: console
---

```{r include=FALSE}

knitr::opts_knit$set(root.dir = "../..")
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", echo=FALSE)

library(tidyverse)
library(volker)
theme_set(theme_bw())

data <- volker::chatgpt
data <- prepare(data)

data$cg_adoption_advantage_01
# Translate labels
data <- data %>% 
  labs_apply(tibble("sd_geschlecht", "Gender")) %>% 
  labs_apply(tibble("sd_alter","Age")) %>% 
  labs_clear(starts_with("cg_adoption_advantage_")) %>% 
  labs_apply(tribble(
    ~item_name, ~item_label, ~value_name, ~value_label,
    "cg_adoption_advantage_01", "Benefits: General", "1", "not at all",
    "cg_adoption_advantage_01", "Benefits: General", "5", "fully applies",
    "cg_adoption_advantage_02", "Benefits: Financial", "1", "not at all",
    "cg_adoption_advantage_02", "Benefits: Financial", "5", "fully applies",
    "cg_adoption_advantage_03", "Benefits: Workplace", "1", "not at all",
    "cg_adoption_advantage_02", "Benefits: Financial", "5", "fully applies",
    "cg_adoption_advantage_04", "Benefits: Joy", "1", "not at all",
    "cg_adoption_advantage_02", "Benefits: Financial", "5", "fully applies",
  )) %>% 
  volker::labs_apply(tibble("in_adoption","Adopter type")) %>%   
  mutate(in_adoption = case_when(
    str_detect(in_adoption,"Ich probiere ") ~ "I try quickly",
    str_detect(in_adoption,"Ich warte eher ab") ~ "I tend to wait",
    str_detect(in_adoption,"wenn ich nicht mehr anders kann") ~ "Only when necessary",
  )) %>%   
  mutate(
    sd_geschlecht = fct_recode(
      sd_geschlecht,
      "male" = "männlich",
      "female" = "weiblich",
      "diverse" = "divers"
    )
  )

```

## 1. One variable

### Frequency table for one categorical variable: Gender
```{r}

data %>% 
  tab_counts(sd_geschlecht)

data %>% 
  plot_counts(sd_geschlecht)

ggsave("plots/examples/plot_counts_one.png", width=300,height=200, units="px", dpi=96)

```

### Distribution table for one metric variable: Age
```{r}

data %>%
  tab_metrics(sd_alter)

data %>%
  plot_metrics(sd_alter)

ggsave("plots/examples/plot_metrics_one.png", width=300,height=200, units="px", dpi=96)

```

## 2. Multiple items

### Frequency table for multiple categorical variables: Adoption factors
```{r}

data %>% 
  filter(
    cg_adoption_advantage_01 < 4,
    cg_adoption_advantage_02 < 4,
    cg_adoption_advantage_03 < 4,
    cg_adoption_advantage_04 < 4
    
  ) %>% 
  tab_counts(starts_with("cg_adoption_advantage_"))

data %>% 
  plot_counts(starts_with("cg_adoption_advantage_")) +
  theme(legend.position = "none")

ggsave("plots/examples/plot_counts_items.png", width=600,height=400, units="px", dpi=96, scale = 0.5)
```

### Distribution table for multiple metric items: Adoption factors
```{r}

data %>% 
  tab_metrics(starts_with("cg_adoption_advantage_"))

data %>% 
  plot_metrics(starts_with("cg_adoption_advantage_"))

ggsave("plots/examples/plot_metrics_items.png", width=600,height=400, units="px", dpi=96, scale = 0.5)
```

## 3. Two variables (one being categorical)

### Cross table of categorical variables: Innovator type by gender

```{r}

data %>% 
  tab_counts(in_adoption, sd_geschlecht)

data %>% 
  filter(sd_geschlecht != "diverse") %>% 
  filter(in_adoption != "Only when necessary") %>% 
  plot_counts(in_adoption, sd_geschlecht, prop="rows") +
  theme(legend.position = "bottom")

ggsave("plots/examples/plot_counts_one_grouped.png", width=300,height=200, units="px", dpi=96, scale = 1)
```

### Group comparison of a metric variable: Age by gender

```{r results='asis'}

tab_metrics(data, sd_alter, sd_geschlecht)

data %>% 
  filter(sd_geschlecht != "diverse") %>% 
  plot_metrics(sd_alter, sd_geschlecht)

ggsave("plots/examples/plot_metrics_one_grouped.png", width=300,height=200, units="px", dpi=96, scale = 1)
```

## 4. Multiple metric variables

### Compare means of multiple items: Adoption factors by gender
```{r results='asis'}

data %>% 
  tab_metrics(
    starts_with("cg_adoption_advantage"), 
    sd_geschlecht
  )

```

### Correlation of items: Adoption factors by adoption factors
```{r results='asis'}

data %>% 
  tab_metrics_items_cor(starts_with("cg_adoption_advantage"))

```
