---
title: "Create example plots and tables"
output: rmarkdown::html_vignette
editor_options: 
  chunk_output_type: console
---

```{r include=FALSE}

knitr::opts_chunk$set(collapse = TRUE, comment = "#>", echo=TRUE)

library(tidyverse)
library(volker)
theme_set(theme_bw())

data <- volker::chatgpt

# Recode -9 to NA
data <- mutate(data, across(starts_with("cg_adoption_"), ~ na_if(.,-9)  ))

# Add label to sd_alter
data <- set_item_labels(data, tibble("sd_alter","Alter")) 

```

## 1. One variable

### Frequency table for one categorical variable: Gender
```{r results='asis'}

data %>% 
  tab_var_counts(sd_geschlecht)

```

### Distribution table for one metric variable: Age
```{r results='asis'}

tab_var_metrics(data, sd_alter)

```

## 2. Multiple items

### Frequency table for multiple categorical variables: Adoption factors
```{r results='asis'}


newlabels <- tribble(
  ~item_name, ~item_label,
  "cg_adoption_advantage_01", "Allgemeine Vorteile",
  "cg_adoption_advantage_02", "Finanzielle Vorteile",
  "cg_adoption_advantage_03", "Vorteile bei der Arbeit",
  "cg_adoption_advantage_04", "Macht mehr Spaß"
)

data %>% 
  set_item_labels(newlabels) %>% 
  filter(
    cg_adoption_advantage_01 < 4,
    cg_adoption_advantage_02 < 4,
    cg_adoption_advantage_03 < 4,
    cg_adoption_advantage_04 < 4
    
  ) %>% 
  tab_item_counts(starts_with("cg_adoption_advantage_"))

```

### Distribution table for multiple metric items: Adoption factors
```{r results='asis'}


data %>% 
  set_item_labels(newlabels) %>% 
  tab_item_metrics(starts_with("cg_adoption_advantage_"))

```

## 3. Two variables (one being categorical)

### Cross table of categorical variables: Innovator type by gender

```{r results='asis'}

data %>% 
  mutate(in_adoption = case_when(
    str_detect(in_adoption,"Ich probiere ") ~ "Ich probiere schnell aus",
    str_detect(in_adoption,"Ich warte eher ab") ~ "Ich warte eher ab",
    str_detect(in_adoption,"wenn ich nicht mehr anders kann") ~ "Erst wenn es sein muss",
  )) %>% 
  volker::set_item_labels(tibble("in_adoption","Adopter type")) %>% 
  tab_group_counts(in_adoption, sd_geschlecht)

```

### Group comparison of a metric variable: Age by gender

```{r results='asis'}

tab_group_metrics(data, sd_alter, sd_geschlecht)

```

## 4. Multiple metric variables

### Compare means of multiple items: Adoption factors by gender
```{r results='asis'}

data %>% 
  set_item_labels(newlabels) %>% 
  tab_multi_means(starts_with("cg_adoption_advantage"), sd_geschlecht)

```

### Correlation of items: Adoption factors by adoption factors
```{r results='asis'}

data %>% 
  set_item_labels(newlabels) %>% 
  tab_multi_corr(starts_with("cg_adoption_advantage"))

```

## Plots

```{r}

# Plots
#plot_compare_factor(data, in_adoption, sd_geschlecht)
# ggsave("plots/plot_compater_factor.png", width = 13, height = 6)

#plot_counts(data, starts_with("cg_adoption_advantage"))
# ggsave("plots/plot_counts2.png", width = 13, height = 6)


```

