---
title: "All kinds of statistics: effect sizes, parameter estimates, p values"
output: volker::html_report
vignette: >
  %\VignetteIndexEntry{Effects}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(volker)
```

```{r}

# Load data 
data <- volker::chatgpt
```

| \# | function                           | implemented | effect calculations                                                                              |
|----|------------------------------------|-------------|--------------------------------------------------------------------------------------------------|
| 1  | effect_counts_one                  |             | Compare to equality (Gini Coefficient, Goodness of fit)                                          |
| 2  | effect_counts_one_grouped          |             | Contingency of two variables (Cramér's V, Chi squared)                                           |
| 3  | effect_counts_one_cor              | not yet     | Explained variance (Pseudo-R-squared of logistic regression)                                     |
| 4  | effect_counts_items                |             | Compare each item to equality (Gini Coefficient, Goodness of fit)                                |
| 5  | effect_counts_items_grouped        |             | Cramer's V and Chi-square-test for each item                                                     |
| 6  | effect_counts_items_grouped_items  |             | Correlation of categorical items with categorical items                                          |
| 7  | effect_counts_items_cor            | not yet     | Explained variance of each item by the metric variable (Pseudo-R-squared of logistic regression) |
| 8  | effect_counts_items_cor_items      | not yet     | Correlation of categorical items with metric items                                               |
| 9  | effect_metrics_one                 |             | Compare to normality (Shapiro-Wilk-Normality-test)                                               |
| 10 | effect_metrics_one_grouped         |             | Explained variance (R squared, t-test)                                                           |
| 11 | effect_metrics_one_cor             |             | Correlation (Pearson's r, Spearman's rho, t-test)                                                |
| 12 | effect_metrics_items               |             | Distribution test for each item (Shapiro-Wilk-Normality-test)                                    |
| 13 | effect_metrics_items_grouped       |             | Explained variance of each item by the grouping variable (R squared)                             |
| 14 | effect_metrics_items_grouped_items | not yet     | Correlation of metric items with categorical items                                               |
| 15 | effect_metrics_items_cor           |             | Correlation between each item and the correlation variable (Pearson's r, Spearman's rho, t-test) |
| 16 | effect_metrics_items_cor_items     |             | Correlation between each item and other items (Pearson's r, Spearman's rho, t-test)              |

# Categorical variables

## 1. Inequality of counts (Chi-squared test for equal distribution, Gini-coefficient)
```{r}
data %>%  
 filter(sd_gender != "diverse") |> 
 effect_counts(sd_gender)
```

## 2. Cross table
```{r}
effect_counts(data, adopter, sd_gender)
```

## 3. Logistic regression with one metric predictor
```{r}
# TODO
#effect_counts(data, adopter, sd_age, metric = TRUE)
```

## 4. Chi-square goodness-of-fit test for each item
```{r}
effect_counts(data, starts_with("cg_adoption_advantage"))
```

## 5. Cramers v and Chi-square-test for each item
```{r}
effect_counts(data, starts_with("cg_adoption_advantage"), sd_gender)
```

## 6. Correlation of categorical items with categorical items
```{r}

effect_counts(data, starts_with("cg_adoption_adv"), starts_with("use_"))

```

## 7. Explained variance of each item by the metric variable (Pseudo-R-squared of logistic regression) 
```{r}
# TODO
#effect_counts(data, starts_with("cg_adoption_advantage"), sd_age)
```

## 8. Correlation of categorical items with metric items

```{r}
# TODO
#effect_counts(data, starts_with("cg_adoption_adv"), starts_with("cg_adoption_adv"), metric = TRUE)
```

# Metric variables

## 9. Normality test for one metric variable
```{r}
effect_metrics(data, sd_age)
```

## 10. T-test / ANOVA
```{r}
effect_metrics(data, sd_age, adopter)

```

## 11. Correlation test
```{r}
effect_metrics(data, sd_age, use_private, metric=T)
```

## 12. Distribution test for each item
```{r}
effect_metrics(data, starts_with("cg_adoption"))
```

## 13. Analysis of variance 
```{r}
effect_metrics(data, starts_with("cg_adoption_"), adopter)
```

## 14. Correlation of metric items with categorical items
```{r}
# TODO: 
# effect_metrics(data, starts_with("cg_adoption_adv"), starts_with("use_"))
```

## 15. Correlation between items and one variable
```{r}
effect_metrics(data, starts_with("cg_adoption"), sd_age, metric = TRUE)
```

## 16. Correlation of metric items with metric items
```{r}

effect_metrics(
  data, 
  starts_with("cg_adoption_adv"),
  starts_with("cg_adoption_adv"),
  metric = TRUE
) 

```


## 17. Multivariable regression
```{r}
data |> 
  filter(sd_gender != "diverse") |> 
  model_metrics_tab(use_work, categorical = c(sd_gender, adopter), metric = c(starts_with("cg_adoption"), sd_age))

data |> 
  filter(sd_gender != "diverse") |> 
  model_metrics_plot(use_work, categorical = c(sd_gender, adopter), metric = c(starts_with("cg_adoption"), sd_age))

```

