---
title: "All kinds of statistics: effect sizes, parameter estimates, p values"
output: volker::html_report
vignette: >
  %\VignetteIndexEntry{Effects}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r include=FALSE}
knitr::opts_chunk$set(
  echo = F,
  knitr.table.format = "html"
)

library(tidyverse)
library(volker)
```

```{r}

# Load data 
ds <- volker::chatgpt
```

| \#      | function                      | implemented | effect size    | confidence intervals                                | significance test |
|---------|-------------------------------|-------------|----------------|-------------------------------------------|-------------------|
| 1       | effect_counts_one            | not yet     | | | |
| 2       | effect_counts_one_grouped    |             | Cramér's V | proportions | Chi squared |
| 3       | effect_counts_one_cor        | not yet     | | | |
| 4       | effect_counts_items          | not yet     | | | |
| 5       | effect_counts_items_grouped  | not yet     | | | |
| 6       | effect_counts_items_cor      | not yet     | | | |
| 7       | effect_metrics_one           | not yet     | | | |
| 8       | effect_metrics_one_grouped   |             | R squared | means | t-test |
| 9       | effect_metrics_one_cor       |             | Pearson's r, Spearman's rho | correlation  | t-test             |
| 10      | effect_metrics_items         |             | R squared | means | t-test             
| 11      | effect_metrics_items_grouped | not yet     |  |  | |
| 12      | effect_metrics_items_cor     |             | Pearson's r, Spearman's rho | correlation | t-test|


```{r}

effect_counts(ds, adopter, sd_gender)
effect_metrics(ds, sd_age, adopter)
effect_metrics(ds, sd_age, use_private, metric=T)
effect_metrics(ds, sd_age, use_private, metric=T)
```
