---
title: "All kinds of statistics: effect sizes, parameter estimates, p values"
output: volker::html_report
vignette: >
  %\VignetteIndexEntry{Effects}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(volker)
```

```{r}

# Load data 
data <- volker::chatgpt
```

| \#      | function                      | implemented | effect size    | confidence intervals                      | significance test |
|---------|-------------------------------|-------------|----------------|-------------------------------------------|-------------------|
| 1       | effect_counts_one            | not yet      |                |                                           |                   |
| 2       | effect_counts_one_grouped    |              | Cramér's V     | proportions                               | Chi squared       |
| 3       | effect_counts_one_cor        | not yet      |                |                                           |                   |
| 4       | effect_counts_items          | not yet      |                |                                           |                   |
| 5       | effect_counts_items_grouped  | not yet      |                |                                           |                   |
| 6       | effect_counts_items_cor      | not yet      |                |                                           |                   |
| 7       | effect_metrics_one           | not yet      |                |                                           |                   |
| 8       | effect_metrics_one_grouped   |              | R squared      | means                                     | t-test            |
| 9       | effect_metrics_one_cor       |              | Pearson's r, Spearman's rho | correlation                  | t-test            |
| 10      | effect_metrics_items         |              | R squared      | means                                     | t-test            | 
| 11      | effect_metrics_items_grouped | not yet      |                |                                           |                   |
| 12      | effect_metrics_items_cor     |              | Pearson's r, Spearman's rho | correlation                  | t-test            |

# 1. Chi-squared test for given probabilites 
```{r}
data <- data %>%  
  filter(sd_gender != "diverse")

effect_counts(data, sd_gender)
```

# 2. Cross table
```{r}
effect_counts(data, adopter, sd_gender)
```


# 3. Logistic regression with one metric predictor
```{r}

# TODO
effect_counts(data, adopter, sd_age, metric = TRUE)
```

# 7. Normality test for one metric variable
```{r}
effect_metrics(data, sd_age)
```


# 8. T-test / ANOVA
```{r}
effect_metrics(data, sd_age, adopter)
```


# 9. Correlation test
```{r}
effect_metrics(data, sd_age, use_private, metric=T)
```


# 10. Correlation within items
```{r}
effect_metrics(data, starts_with("cg_adoption"))
```


# 12. Correlation between items and one variable
```{r}
effect_metrics(data, starts_with("cg_adoption"), sd_age, metric = TRUE)
```
