---
title: "Introduction"
output: volker::html_report
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r include=FALSE}
knitr::opts_chunk$set(
  comment = "", 
  echo = TRUE
)

# Load the packages
library(dplyr)
library(ggplot2)
library(volker)

# Set the basic plot theme
theme_set(theme_bw())
```


```{r include=FALSE}

# Load example data from the package
data <- volker::chatgpt

```

## How to generate tables and plots?

The plot and table type is determined by your column selection. Try it out!

### Categorical variables

```{r}
# A single variable
tab_counts(data, use_private)
```

```{r}
# A list of variables
tab_counts(data, c(use_private, use_work))
```

```{r}
# Variables matched by a pattern
tab_counts(data, starts_with("use_"))
```


### Metric variables

To select the approriate function, you need to decide whether your data 
is categorical or metric.

```{r}
# One metric variable
tab_metrics(data, sd_age)
```

```{r fig.width=6, fig.height=8}

# Multiple metric items
tab_metrics(data, starts_with("cg_adoption_"))
plot_metrics(data, starts_with("cg_adoption_"))

```

### Cross tabulation and group comparison

Provide a grouping column in the third parameter to compare different groups.

```{r}
tab_counts(data, adopter, sd_gender)
```

In the corresponding plot function, you can use the prop parameter to grow bars to 100%.
The numbers parameter prints the percentages onto the bars.

```{r}
data |> 
  filter(sd_gender != "diverse") |> 
  plot_counts(adopter, sd_gender, prop="rows", numbers="p")
```

For metric variables, you can compare the mean values.

```{r}
# Compare the means of one variable
tab_metrics(data, sd_age, sd_gender)
```

```{r}
# Compare the means of multiple items
tab_metrics(data, starts_with("cg_adoption_"), sd_gender)
```


# Automatically generate reports

Reports combine plots and tables. Optionally, for item batteries, an index is calculated and reported.

To see an example or develop own reports, use the volker report template in RStudio:

- Create a new R Markdown document from the main menu  
- In the popup select the "From Template" option  
- Select the volker template.  
- The template contains a working example. 
  Just click knit to see the result.

Have fun with developing own reports!

Alternatively, manually add `volker::html_report` to the 
output options of your Markdown document:

```
---
title: "How to create reports?"
output: 
  volker::html_report
---
```

Then, you can generate combined outputs using the report-functions.
One advantage of the report-functions is that plots are automatically 
scaled to fit the page.

The main entry point for reports are the report-functions.
See the function help or the report vignette for further options.

```{r}

data %>% 
  filter(sd_gender != "diverse") %>% 
  report_metrics(starts_with("cg_adoption_"), sd_gender)

```


If you want to add content before the report outputs, 
set the title parameter to `FALSE` and add your 
own title.

A good place for methodological details is a tabsheet 
next to the "Plot" and the "Table" buttons. You can add a tab
by setting the close-parameter to `FALSE` and adding a new header
on the fifth level (5 x # followed by the tab name). Close your new tabsheet with
`#### {-}` (4 x #). See the example Markdown behind this vignette.

### Adoption types

```{r}
data %>% 
  filter(sd_gender != "diverse") %>% 
  report_counts(adopter, sd_gender, prop="rows", title= FALSE, close= FALSE)
```


##### Method
Basis: Only male and female respondents.

#### {-}


# Customizing outputs

Plot and table functions share a number of parameters that can be used to customize the outputs. Lookup the available parameters in the help of the specific function:

- labels: Labels are extracted from the column attributes, if present. Set to FALSE to output bare column names and values.  
- title: All plots usually get a title derived from the column attributes or column names. Set to FALSE to suppress the title or provide a title of your choice as a character value.  
- percent: Frequency tables show percentages by default. Set to FALSE to get raw proportions - easier to postprocess in further calculations.
- digits: Tables containing means and standard deviations by default round values to one digit. Increase the number to show more digits.
- numbers: Bar plots give quick impressions, tables provide exact numbers. In bar charts you can combine both and print the frequencies onto the bars. Set the numbers parameter to "n", "p" or c("n","p"). To prevent cluttering and overlaps, numbers are only plotted on bars larger than 5%.
- values: The more variables you desire, the denser the output must be. Some tables try to serve you insights at the maximum and show two values in one cell, for example the absolute counts (n) and the percentages (p), or the mean (m) and the standard deviation (sd). Control your desire with the values-parameter.
- prop: Calculating percentages in a cross tab requires careful selection of the base. You can choose between total, row or column percentages. For stacked bar charts, displaying row percentages instead of total percentages gives a direct visual comparison of groups.
- negative: In surveys, negative values such as -9 or -2 are often used to mark missing values or residual answers ("I don't know"). Therefore, all metric tables and plots remove negative values before calculation distribution parameters such as the mean. Set negative to TRUE for including those values. By the way: The handy prepare()-function can be used to recode all -9 to NA in a dataset.
- missings: The number of missing values is an important indicator for data quality. In reports, the missings usually are ommited and so do the package functions by default. For data set statics - for example when you monitor an ongoing survey or prepare a data set - you should set the missings-parameter to TRUE if the function supports it.
- ordered: Sometimes categories have an order, from low to high or from few to many. It helps visual inspections to plot ordered values with shaded colors instead of arbitrary colors. For frequency plots, you can inform the method about the desired order. By default the functions try to automatically detect a sensitive order.
- limits: Do you know how to create misleading graphs? It happens when you truncate the minimum or maximum value in a scale. The scale limits are automatically guessed by the package functions (work in progress). Use the limits-parameter to manually fix any misleading graphs.

# Custom labels: Where do they come from?

Labels used in plots and tables are stored in the comment attribute of the variable. 
You can inspect all labels using the `codebook()`-function:

```{r}
codebook(data)
```

You can set custom or new labels with `labs_apply()` by providing a tibble 
with item names in the first column and item labels in the second column.

```{r}
newlabels <- tribble(
  ~item_name, ~item_label,
  "cg_adoption_advantage_01", "Allgemeine Vorteile",
  "cg_adoption_advantage_02", "Finanzielle Vorteile",
  "cg_adoption_advantage_03", "Vorteile bei der Arbeit",
  "cg_adoption_advantage_04", "Macht mehr Spaß"
)

data %>%
  labs_apply(newlabels) %>%
  tab_metrics_items(starts_with("cg_adoption_advantage_"))


```


You can remove all labels with `labs_clear()` to get a plain dataset.

```{r}
data %>%
  labs_clear(everything()) %>%
  tab_counts(starts_with("cg_adoption_advantage_"))
```

With the labels parameter, you achieve a similar result.

```{r}
data %>%
  tab_counts(starts_with("cg_adoption_advantage_"), labels= FALSE)
```


# Scales

You can calculate mean indexes from a bunch of items using `idx_add()`. 
A new column is created with the average value of all selected columns
for each case. 

Reliability and number of items are calculated with `psych::alpha()`
and stored as column attribute named "psych.alpha". The reliability values 
are printed by `tab_metrics()`.

**Add a single index**
```{r}
data %>%
  idx_add(starts_with("cg_adoption_")) %>%
  tab_metrics(idx_cg_adoption)
```

**Compare the index values by group**
```{r}
data %>%
  idx_add(starts_with("cg_adoption_")) %>%
  tab_metrics(idx_cg_adoption, adopter)
```

**Add multiple indizes and summarize them**
```{r}
data %>%
  idx_add(starts_with("cg_adoption_")) %>%
  idx_add(starts_with("cg_adoption_advantage")) %>%
  idx_add(starts_with("cg_adoption_fearofuse")) %>%
  idx_add(starts_with("cg_adoption_social")) %>%
  tab_metrics(starts_with("idx_cg_adoption"))
```


# What's behind the scenes?

The volker-package is based on standard methods for data handling and visualisation. 
You can produce all outputs with a handful of functions. The package just makes your
code dry - don't repeat yourself - and wraps often used snippets into a simple interface.

Basically, all table values are calculated two tidyverse functions:

- count() is used to produce counts  
- skim() is used to produce metrics  

To shape the data frames, two essential functions come into play:  

- group_by() is used to calculate grouped outputs
- pivot_longer() brings multiple items into a format where the item name becomes a grouping variable.  

Plots are generated by `ggplot()`.

The package provides print- and knit-functions that pimp console and markdown output. 
To make this work, the cleanded data, produced plots, tables and markdown snippets gain new classes (`vlkr_df`, `vlkr_plt`, `vlkr_tbl`, `vlkr_rprt`).
