---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: inline
---

```{r include=FALSE}

knitr::opts_chunk$set(comment = "", echo=TRUE)

library(tidyverse)
library(volker)
theme_set(theme_bw())

data <- volker::chatgpt

# Recode -9 to NA
data <- mutate(data, across(starts_with("cg_adoption_"), ~ na_if(.,-9)  ))

# Add label to sd_alter
data <- set_item_labels(data, tibble("sd_alter","Alter")) 

```

## 1. One variable


### Frequency table for one categorical variable: Gender
```{r, results='asis'}

tab_var_counts(data, sd_geschlecht)

```

### Distribution table for one metric variable: Age
```{r, results='asis'}

tab_var_metrics(data, sd_alter)

```

## 2. Multiple items

### Frequency table for multiple categorical variables: Adoption factors
```{r, results='asis'}

tab_item_counts(data, starts_with("cg_adoption_"))

```

### Distribution table for multiple metric items: Adoption factors
```{r, results='asis'}

tab_item_metrics(data, starts_with("cg_adoption_"))

```

## 3. Two variables (one being categorical)

### Cross table of categorical variables: Innovator type by gender

```{r, results='asis'}

tab_group_counts(data, in_adoption, sd_geschlecht)

```

### Group comparison of a metric variable: Age by gender

```{r, results='asis'}

tab_group_metrics(data, sd_alter, sd_geschlecht)

```

## 4. Multiple metric variables

### Compare means of multiple items: Adoption factors by gender
```{r, results='asis'}

tab_multi_means(data, starts_with("cg_adoption_"), sd_geschlecht)

```

### Correlation of items: Adoption factors
```{r, results='asis'}

tab_multi_corr(data, starts_with("cg_adoption_adv"))

tab_multi_corr(data, starts_with("cg_adoption_adv"),starts_with("cg_nutzen"))

```

# Set custom item labels

Item labels are stored in the comment attribute of an item variable. 
When printing item tables, the labels are used. You can set custom or 
new labels by providing a tibble with item names in the first column
and item labels in the second.

```{r, results='asis'}

newlabels <- tribble(
  ~item_name, ~item_label,
  "cg_adoption_advantage_01", "Allgemeine Vorteile",
  "cg_adoption_advantage_02", "Finanzielle Vorteile",
  "cg_adoption_advantage_03", "Vorteile bei der Arbeit",
  "cg_adoption_advantage_04", "Macht mehr Spaß"
)

data %>% 
  set_item_labels(newlabels) %>% 
  tab_item_metrics(starts_with("cg_adoption_advantage_"))

```

# Automatically create reports

Given a list aof column prefixes, you can automatically output frequency tables and plots:  

- If the prefix matches a single column, tab_var_counts() and plot_var_counts() will be used.
- If the prefix matches multiple columns, tab_item_counts() and plot_item_counts() will be used.

```{r, results='asis'}

report(
  data, 
  c(
    "cg_adoption_advantage_", 
    "sd_geschlecht"
  )
)

```

