---
title: "Introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r include=FALSE}

knitr::opts_chunk$set(collapse = TRUE, comment = "#>", echo=TRUE)

library(tidyverse)
library(volker)
theme_set(theme_bw())

data <- volker::chatgpt

# Recode -9 to NA
data <- mutate(data, across(starts_with("cg_adoption_"), ~ na_if(.,-9)  ))

```

## 1. One variable

### Frequency table for one categorial variable: Gender
```{r results='asis'}

tab_var_counts(data, sd_geschlecht)

```

### Distribution table for one metric variable: Age
```{r results='asis'}

tab_var_metrics(data, sd_alter)

```

## 2. Multiple items

### Frequency table for multiple categorial variables: Adoption factors
```{r results='asis'}

tab_item_counts(data, starts_with("cg_adoption_"))

```

### Distribution table for multiple metric items: Adoption factors
```{r results='asis'}

tab_item_metrics(data, starts_with("cg_adoption_"))

```

## 3. Two variables (one being categorical)

### Cross table of categorial variables: Innovator type by gender

```{r results='asis'}

tab_group_counts(data, in_adoption, sd_geschlecht)

```

### Group comparison of a metric variable: Age by gender

```{r results='asis'}

tab_group_metrics(data, sd_alter, sd_geschlecht)

```

## 4. Multiple metric variables

### Compare means of multiple items: Adoption factors by gender
```{r results='asis'}

tab_multi_means(data, starts_with("cg_adoption_"), sd_geschlecht)

```

### Correlation of items: Adoption factors by adoption factors
```{r results='asis'}

tab_multi_corr(data, starts_with("cg_adoption_"))

```
