
---
title: "Labeling"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Labeling}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", echo = TRUE, fig.width = 7, fig.height = 5)

library(dplyr)
library(volker)

ds <- volker::chatgpt

```

```{css, echo=FALSE}
table {margin-left:0 !important;}
```


# The codebook function

Labels used in plots and tables are stored in the comment attribute of the variable. 
You can inspect all labels using the `codebook()`-function:

```{r}
codebook(ds)
```


To conveniently manage all labels of a dataset, 
you can save the result of `codebook()` to an Excel file,
change the labels manually in a copy of the Excel file, 
and finally call `labs_apply()` with your revised codebook.

```{r, eval = FALSE}

library(readxl)
library(writexl)

# Save codebook to a file
codes <- codebook(ds)
write_xlsx(codes,"codebook.xlsx")

# Load and apply a codebook from a file
codes <- read_xlsx("codebook_revised.xlsx")
ds <- labs_apply(codebook)

```


# Change labels of selected items

You can set specific column labels by providing a named list to the items-parameter of `labs_apply()`:


```{r}
ds %>%
  labs_apply(
    items = list(
      "cg_adoption_advantage_01" = "Allgemeine Vorteile",
      "cg_adoption_advantage_02" = "Finanzielle Vorteile",
      "cg_adoption_advantage_03" = "Vorteile bei der Arbeit",
      "cg_adoption_advantage_04" = "Macht mehr Spaß"
    )
  ) %>% 
  tab_metrics(starts_with("cg_adoption_advantage_"))

```


Alternatively, you can use a dataframe in the codebook format.
In this case, provide a tibble with item names in the first column and item labels in the second column.

The tribble function is a convenient way to construct the label tibble.

```{r}
newlabels <- tribble(
  ~item_name, ~item_label,
  "cg_adoption_advantage_01", "Allgemeine Vorteile",
  "cg_adoption_advantage_02", "Finanzielle Vorteile",
  "cg_adoption_advantage_03", "Vorteile bei der Arbeit",
  "cg_adoption_advantage_04", "Macht mehr Spaß"
)

ds %>%
  labs_apply(newlabels) %>%
  tab_metrics(starts_with("cg_adoption_advantage_"))


```


# Change labels of values in selected columns

Data values usally come in two forms: 

- Uncoded: Character values and factor values as well as metric values 
  such as the age of a person can be analyzed and reported without further labeling. 
  The values in the dataset speak for themselves. Usually you don't relabel the values, 
  you change them directly in the dataset.
- Coded: Sometimes data values are numerically coded, for example from 1=disagree to 5 =agree. 
  The values need to be labeled for reporting and interpretation.

Labels for both, coded and uncoded values, can be adjusted by providing a named list to the values-parameter of `labs_apply()`. In addition, select the columns where value labels should be changed:


## Coded values example
```{r}

ds %>%
  labs_apply(
    cols=starts_with("cg_adoption"),  
    values = list(
      "1" = "Stimme überhaupt nicht zu",
      "2" = "Stimme nicht zu",
      "3" = "Unentschieden",
      "4" = "Stimme zu",
      "5" =  "Stimme voll und ganz zu"
    ) 
  ) %>% 
  plot_metrics(starts_with("cg_adoption"))

```

## Uncoded (factor) values example
```{r}
ds %>%
  labs_apply(
    cols=sd_gender,  
    values = list(
      "female" = "Weiblich",
      "male" = "Männlich",
      "diverse" = "Divers"
    ) 
  ) |> 
  plot_counts(sd_gender) 

```

*Hint*: To see the raw unlabeled values, call plot, tab, or report functions with the labels-parameter set to FALSE,
e.g. `plot_counts(ds, starts_with("cg_adoption"), labels = FALSE)`.

Alternatively, construct a tibble in codebook format,
with the columns value_name and value_label. 
Tell `labs_apply()` in which columns value labels should be changed 
and set the values-parameter to TRUE.

```{r}

newlabels <-  tribble(
  ~value_name, ~value_label,
  1, "Stimme überhaupt nicht zu",
  2, "Stimme nicht zu",
  3, "Unentschieden",
  4, "Stimme zu",
  5, "Stimme voll und ganz zu"
)  

ds |> 
  labs_apply(newlabels, cols=starts_with("cg_adoption")) |> 
  plot_metrics(starts_with("cg_adoption"))

```

