
---
title: "Table variations"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Table variations}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", echo = TRUE)

library(dplyr)
library(volker)

ds <- volker::chatgpt

```

```{css, echo=FALSE}
table {margin-left:0 !important;}
```


# The codebook function

Labels used in plots and tables are stored in the comment attribute of the variable. 
You can inspect all labels using the `codebook()`-function:

```{r}
codebook(ds)
```


To conveniently manage all labels of a dataset, 
you can save the result of `codebook()` to an Excel file,
change the labels manually in a copy of the Excel file, 
and finally call `labs_apply()` with your revised codebook.

```{r, eval = FALSE}

library(readxl)
library(writexl)

# Save codebook to a file
codes <- codebook(ds)
write_xlsx(codes,"codebook.xlsx")

# Load and apply a codebook from a file
codes <- read_xlsx("codebook_revised.xlsx")
ds <- labs_apply(codebook)

```


# Change labels of items

You can set column labels by providing a named list to the items-parameter of `labs_apply()`:


```{r}
ds %>%
  labs_apply(
    items = list(
      "cg_adoption_advantage_01" = "Allgemeine Vorteile",
      "cg_adoption_advantage_02" = "Finanzielle Vorteile",
      "cg_adoption_advantage_03" = "Vorteile bei der Arbeit",
      "cg_adoption_advantage_04" = "Macht mehr Spaß"
    )
  ) %>% 
  tab_metrics(starts_with("cg_adoption_advantage_"))

```


Alternatively you can use a dataframe in the codebook format.
In this case, provide a tibble with item names in the first column and item labels in the second column.

The tribble function is a convenient way to construct the label tibble.

```{r}
newlabels <- tribble(
  ~name, ~label,
  "cg_adoption_advantage_01", "Allgemeine Vorteile",
  "cg_adoption_advantage_02", "Finanzielle Vorteile",
  "cg_adoption_advantage_03", "Vorteile bei der Arbeit",
  "cg_adoption_advantage_04", "Macht mehr Spaß"
)

ds %>%
  labs_apply(newlabels) %>%
  tab_metrics(starts_with("cg_adoption_advantage_"))


```


# Change labels of values

Data values usally come in two forms: 

- Uncoded: Character values and factor values as well as metric values 
  such as the age of a person can be analyzed and reported without further labeling. 
  The values in the dataset speak for themselves.
- Coded: Sometimes data values are numerically coded, for example from 1=disagree to 5 =agree. 
  The values need to be labeled for reporting and interpretation.

Since labels and values are identical for uncoded values, you need to change them directly in the dataframe, for example
using Tidyverse functions. 

Labels for coded values can be adjusted by providing a named list to the values-parameter of `labs_apply()`. 
In addition, select the columns where value labels should be changed:


```{r}
ds %>%
  labs_apply(
    cols=starts_with("cg_adoption"),  
    values = list(
      "1" = "Stimme überhaupt nicht zu",
      "2" = "Stimme nicht zu",
      "3" = "Unentschieden",
      "4" = "Stimme zu",
      "5" =  "Stimme voll und ganz zu"
    ) 
  ) %>% 
  plot_metrics(starts_with("cg_adoption"))

```



Alternatively, you can construct a tibble in codebook format,
with the columns value_name and value_label. 
Tell `labs_apply()` in which columns value labels should be changed 
and set the values-parameter to TRUE.

```{r}

ds |> 
  labs_apply(
    tribble(
      ~value_name, ~value_label,
      1, "Stimme überhaupt nicht zu",
      2, "Stimme nicht zu",
      3, "Unentschieden",
      4, "Stimme zu",
      5, "Stimme voll und ganz zu"
    ), 
    cols=starts_with("cg_adoption"),
    values=TRUE
  ) |> 
  plot_metrics(starts_with("cg_adoption"))

```

