---
title: "Linear modeling: Multivariable regression"
output: volker::html_report
vignette: >
  %\VignetteIndexEntry{Effects}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r include=FALSE}
knitr::opts_chunk$set(echo = F)

library(tidyverse)
library(volker)
```

```{r}

# Load data 
data <- volker::chatgpt
data <- filter(data, sd_gender != "diverse") 
```

## One categorical and one metric independent variable

The report_metrics-method generates everything needed for a basic linear model. 
Other common terms for linear modeling are regression analysis or analysis of variance.

- As always with volker package functions, the first parameter is the dataset.
- The second parameter holds the variable of interest: Provide the variable to be explained (the dependent variable).
- Set the `model` parameter to `TRUE`. Optionally, output regression diagnostics using the respective parameter.

Other parameters determine the independent variables:  
- The cross parameter (3th parameter) always holds categorical variables such as gender.
- The metric parameter (4th parameter) is used to provide a selection of metric independent variables such as age.
- In case of interaction terms, add them to the interactions parameter (see example below, e.g. `c(sd_gender * sd_age)`)  


```{r echo=TRUE}

report_metrics(data, use_work, cross = sd_gender, metric = sd_age, model = TRUE, diagnostics = TRUE)

```


## Multiple categorical and metric independent variables
```{r echo=TRUE}

report_metrics(
  data,
  use_work, 
  cross  = c(sd_gender, adopter), 
  metric = c(starts_with("cg_adoption"), sd_age), 
  model      = TRUE,
  diagnostics = TRUE
)

```


## Index as independent variable

```{r echo=TRUE}

data |> 
  add_index(starts_with("cg_adoption")) |> 
  report_metrics(
    use_work, 
    cross  = c(sd_gender, adopter), 
    metric = c(idx_cg_adoption, sd_age),
    model = TRUE
  )

```


## Interactions
```{r echo=TRUE}

data |> 
  report_metrics(
    use_work, 
    cross        = c(sd_gender), 
    metric       = c(sd_age),
    interactions = c(sd_gender * sd_age),
    model = TRUE
  )

```

## Add predicted values to data frame

To use the predicted values, first add the model. 
This will result in a new column with the prefix "prd_".

Instead of using the report-method, you can explicitly request the results 
using `model_tab()` and `model_plot()`.


```{r echo=TRUE}

data <- add_model(
  data, 
  use_work, 
  categorical = c(sd_gender), 
  metric = c(use_private),
  interactions = c(sd_gender * use_private)
)

model_tab(data, prd_use_work)
model_plot(data, prd_use_work)
```

After adding predicted values, you can use them as any other column. 
The following example generates a scatter plot to inspect how well the
predicted values correlate with the true values.


```{r}

report_metrics(data, use_work, prd_use_work, metric = TRUE, jitter = TRUE)

```

