---
title: "Plot variations"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Plot variations}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console

---

```{r include=FALSE}
knitr::opts_chunk$set(
   echo = TRUE,
   fig.width=7
)

library(dplyr)
library(ggplot2)
library(volker)

theme_set(theme_vlkr())

# Load data
data <- volker::chatgpt

```

## Frequencies of categorical variables

### 1. One variable: Frequency plot of Gender
```{r}
plot_counts(data, sd_gender)
```

### 2. Two variables: Stacked frequency plot of innovator type by gender

```{r}
# The prop parameter grows bars to 100%
# The numbers parameter adds percentages to the bars

plot_counts(data, adopter, sd_gender, prop = "rows", number="p")
```


### 3. Multiple items: Frequency plot for adoption factors
```{r, fig.height=6}
# The numbers parameter adds percentages to the bars
plot_counts(data, starts_with("cg_adoption_"), numbers = "p")

```


### 4. Multiple items: Frequency plot for adoption factors grouped by adopter category
```{r, fig.height=6}

# # TODO: Coding style: fix whitespace in function call
# plot_counts_items_grouped(
#   data, starts_with("cg_adoption_"), adopter,   category=c(4,5),
#   numbers = "n"
# )

```


## Metric distributions

### 1. Distribution for one metric variable: Age
```{r}
plot_metrics(data, sd_age)
```


### 2. Distribution by a grouping variable
```{r}
plot_metrics(data, sd_age, sd_gender, bars="box")
```


### 3. Distribution of multiple metric items: Adoption factors
```{r, fig.height=6}
# Note that negative values are omitted,
# you can change the behavior with the negative-parameter
plot_metrics(data, starts_with("cg_adoption_"))
```

### 4. Group comparison of multiple metric items: Adoption factors by gender
```{r, fig.height=6}
# Filter out one group, too few cases in the sample
data %>% 
  filter(sd_gender != "divers") %>% 
  plot_metrics(starts_with("cg_adoption_"), sd_gender)
```

## 5. Correlation of multiple items with one metric variable
```{r}

plot_metrics(data, starts_with("cg_adoption_social"), sd_age, metric = T) 

plot_metrics_items_cor(data, starts_with("cg_adoption_adv"), sd_age)

```

### 6. Correlation of multiple items
```{r}
# TODO: Fix heading level ("## 5. Correlation of multiple items" one level down)
plot_metrics(data, starts_with("cg_adoption_social"), starts_with("cg_adoption_"), numbers=T)

```
