---
title: "Plot variations"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Plot variations}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console

---

```{r include=FALSE}
knitr::opts_chunk$set(
   echo = TRUE,
   fig.width=7
)

library(dplyr)
library(ggplot2)
library(volker)

theme_set(theme_vlkr())

# Load data
data <- volker::chatgpt

```


| \#     | function                     | implemented | output | scale    | columns  | crossings  |
|--------|------------------------------|-------------|--------|----------|-----------|-------------|
| 1     | plot_counts_one              |             | plot   | counts   | one       |             |
| 2     | plot_counts_one_grouped    |             | plot   | counts   | one       | grouped     |
| 3     | plot_counts_one_cor         | not yet     | plot   | counts   | one       | correlated |
| 4     | plot_counts_items          |             | plot   | counts   | multiple |             |
| 5     | plot_counts_items_grouped  |      | plot   | counts   | multiple | grouped    |
| 6     | plot_counts_items_cor       | not yet     | plot   | counts   | multiple | correlated |
| 7     | plot_metrics_one           |             | plot   | metrics | one       |             |
| 8     | plot_metrics_one_grouped   |             | plot   | metrics | one       | grouped    |
| 9     | plot_metrics_one_cor        |      | plot   | metrics | one       | correlated |
| 10    | plot_metrics_items          |             | plot   | metrics | multiple |             |
| 11    | plot_metrics_items_grouped |             | plot   | metrics | multiple | grouped    |
| 12    | plot_metrics_items_cor      | not yet      | plot   | metrics | multiple | correlated |


## Frequencies of categorical variables

### 1. One variable: Frequency plot of Gender
```{r}
plot_counts(data, sd_gender)
```

### 2. Two variables: Stacked frequency plot of innovator type by gender
```{r}
# The prop parameter grows bars to 100%
# The numbers parameter adds percentages to the bars

plot_counts(data, adopter, sd_gender, prop = "cols", number="p")
```

### 3. Group probabilities by a metric variable
```{r}
# TODO
# plot_metrics(data, sd_gender, sd_age)
```

### 4. Multiple items: Frequency plot for adoption factors
```{r, fig.height=6}
# The numbers parameter adds percentages to the bars
plot_counts(data, starts_with("cg_adoption_"), numbers = "p")
```

### 5. Multiple items: Frequency plot for adoption factors grouped by adopter category
```{r, fig.height=6}

options(vlkr.wrap.labels=30)
options(vlkr.wrap.legend=10)

plot_counts(
  data, starts_with("cg_adoption_"), adopter,
  category=c("agree", "strongly agree")
)

```

### 6. Group probabilities of multiply items by a metric variable
```{r}
# TODO
# plot_counts(data, starts_with("use_"), sd_age)
```


## Metric distributions

### 7. Distribution for one metric variable: Age
```{r}
plot_metrics(data, sd_age)
```


### 8. Distribution by a grouping variable
```{r}
plot_metrics(data, sd_age, sd_gender, bars="box")
```

### 9 Correlation of two metric variables
```{r}
plot_metrics(data, use_private, sd_age, metric=TRUE)
```

### 10. Distribution of multiple metric items: Adoption factors
```{r, fig.height=6}
# Note that negative values are omitted,
# you can change the behavior with the negative-parameter
plot_metrics(data, starts_with("cg_adoption_"))
```

### 11. Group comparison of multiple metric items: Adoption factors by gender
```{r, fig.height=6}
# Filter out one group, too few cases in the sample
data %>% 
  filter(sd_gender != "divers") %>% 
  plot_metrics(starts_with("cg_adoption_"), sd_gender)
```

### 12. Correlation of items with one single variable

```{r}
#TODO
#plot_metrics(data, starts_with("cg_adoption_adv"), sd_age, metric=T)
```
