---
title: "Plot variations"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Plot variations}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", echo = TRUE)

library(tidyverse)
library(volker)
theme_set(theme_bw())

data <- volker::chatgpt


# Recode -9 to NA
data <- mutate(data, across(starts_with("cg_adoption_"), ~ na_if(., -9)))

# Add label to sd_alter
data <- set_item_labels(data, tibble("sd_alter", "Alter"))
```

## Frequencies of categorical variables

### 1. One variable: Frequency plot of Gender
```{r results='asis'}
plot_var_counts(data, sd_geschlecht)
```

### 2. Multiple items: Frequency plot for adoption factors
```{r results='asis'}
# Use the .numbers parameter to add counts to the bars
plot_item_counts(data, starts_with("cg_adoption_"), numbers = "n")
```

### 3. Two variables: Stacked frequency plot of innovator type by gender

```{r results='asis'}
# TODO: use number=c("n","p")
plot_group_counts(data, in_adoption, sd_geschlecht, prop = "rows")
```

## Metric distributions

### 1. Distribution for one metric variable: Age
```{r results='asis'}
plot_var_metrics(data, sd_alter)
```


### 2. Distribution of multiple metric items: Adoption factors
```{r results='asis'}
# Note that negative values are omitted,
# you can change the behavior with the .negative parameter
plot_item_metrics(data, starts_with("cg_adoption_"))
```

### 3. Distribution by a grouping variable
```{r results='asis'}
plot_group_metrics(data, sd_alter, sd_geschlecht)
plot_multi_means(data, starts_with("cg_adoption_"), sd_geschlecht)
```

### 4. Index  distribution by a grouping variable
```{r results='asis'}
data %>%
  add_idx(starts_with("cg_adoption_social_")) %>%
  add_idx(starts_with("cg_adoption_fearofuse_")) %>%
  add_idx(starts_with("cg_adoption_advantage_")) %>%
  # Set new labels for the three index columns
  set_col_label(starts_with("idx_cg_adoption"), c(
    "ChatGPT-Erwartung: Social",
    "ChatGPT-Erwartung: Fear of Use",
    "ChatGPT-Erwartung: Advantage"
  )) %>%
  plot_multi_means(starts_with("idx_cg_adoption"), in_adoption)
```

