---
title: "Plot variations"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Plot variations}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console

---

```{r include=FALSE}
knitr::opts_chunk$set(
   echo = FALSE,
   include=TRUE,
   fig.width=8
)

library(tidyverse)
library(volker)
theme_set(theme_bw())

# Load data
data <- volker::chatgpt

# Recode -9 to NA
data <- prepare(data)

# Add label to sd_alter
data <- set_col_labels(data, sd_alter, c("Alter"))

```

## Frequencies of categorical variables

### 1. One variable: Frequency plot of Gender
```{r}
plot_counts_one(data, sd_geschlecht)
```

### 2. Multiple items: Frequency plot for adoption factors
```{r}

# Use the numbers parameter to add counts to the bars
plot_counts_items(data, starts_with("cg_adoption_"), numbers = "p")

```

### 3. Two variables: Stacked frequency plot of innovator type by gender

```{r}
# TODO: use number=c("n","p")
plot_counts_one_grouped(data, in_adoption, sd_geschlecht, prop = "rows")
```

## Metric distributions

### 1. Distribution for one metric variable: Age
```{r}

plot_metrics_one(data, sd_alter)

```


### 2. Distribution of multiple metric items: Adoption factors
```{r}

# Note that negative values are omitted,
# you can change the behavior with the negative-parameter
plot_metrics_items(data, starts_with("cg_adoption_"))

```

### 3. Distribution by a grouping variable
```{r}
plot_metrics_one_grouped(data, sd_alter, sd_geschlecht)
```


```{r}
plot_metrics_items_grouped(data, starts_with("cg_adoption_"), sd_geschlecht)
```

### 4. Index  distribution by a grouping variable
```{r}

data %>%
  add_idx(starts_with("cg_adoption_social_")) %>%
  add_idx(starts_with("cg_adoption_fearofuse_")) %>%
  add_idx(starts_with("cg_adoption_advantage_")) %>%
  
  # Set new labels for the three index columns
  set_col_label(starts_with("idx_cg_adoption"), c(
    "ChatGPT-Erwartung: Social",
    "ChatGPT-Erwartung: Fear of Use",
    "ChatGPT-Erwartung: Advantage"
  )) %>%
  
  select(starts_with("idx_"), in_adoption) %>% 
  plot_metrics_items_grouped(starts_with("idx_cg_adoption"), in_adoption)
  
```

