---
title: "Plot variations"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Plot variations}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console

---

```{r include=FALSE}
knitr::opts_chunk$set(
   echo = TRUE,
   fig.width=7
)

library(tidyverse)
library(volker)
theme_set(theme_bw())

# Load data
data <- volker::chatgpt

```

## Frequencies of categorical variables

### 1. One variable: Frequency plot of Gender
```{r}
plot_counts(data, sd_gender)
```

### 2. Two variables: Stacked frequency plot of innovator type by gender

```{r}
# The prop parameter grows bars to 100%
# The numbers parameter adds percentages to the bars
plot_counts(data, adopter, sd_gender, prop = "rows", number="p")
```


### 3. Multiple items: Frequency plot for adoption factors
```{r, fig.height=6}
# The numbers parameter adds percentages to the bars
plot_counts(data, starts_with("cg_adoption_"), numbers = "p")

```


## Metric distributions

### 1. Distribution for one metric variable: Age
```{r}
plot_metrics(data, sd_age)
```


### 2. Distribution by a grouping variable
```{r}
plot_metrics(data, sd_age, sd_gender)
```


### 3. Distribution of multiple metric items: Adoption factors
```{r, fig.height=6}
# Note that negative values are omitted,
# you can change the behavior with the negative-parameter
plot_metrics(data, starts_with("cg_adoption_"))
```

### 4. Group comparison of multiple metric items: Adoption factors by gender
```{r, fig.height=6}
# Filter out one group, too few cases in the sample
data %>% 
  filter(sd_gender != "divers") %>% 
  plot_metrics(starts_with("cg_adoption_"), sd_gender)
```

### 4. Index  distribution by a grouping variable
```{r}

data %>%
  add_idx(starts_with("cg_adoption_social_")) %>%
  add_idx(starts_with("cg_adoption_fearofuse_")) %>%
  add_idx(starts_with("cg_adoption_advantage_")) %>%
  
  # Set new labels for the three index columns
  labs_apply(tribble(
    ~item_name,                  ~item_label,
    "idx_cg_adoption_social",    "Erwartung: Soziales",
    "idx_cg_adoption_fearofuse", "Erwartung: Ängste",
    "idx_cg_adoption_advantage", "Erwartung: Vorteile"
  )) %>%
  
  plot_metrics(starts_with("idx_cg_adoption"), adopter)
  
```

