---
title: "How to create volker reports?"
output: 
  volker::html_report
vignette: >
  %\VignetteIndexEntry{Reports}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r include=FALSE}

# Markdown options
knitr::opts_chunk$set(echo = TRUE, include=T)

# Load packages
library(tidyverse)
library(volker)
theme_set(theme_bw())

# Load example data
data <- volker::chatgpt
```

Reports combine graphs, tables, indexes and additional output.´
The volker package comes with a Markdown template that generates 
interactive HTML documents in which you can switch between 
the different parts of the report.

How to use the template:
- Create a new R Markdown document from the menu
- Select "From template"

Alternatively, manually add `volker::html_report` to the 
output options of your Markdown document:


```
---
title: "How to create reports?"
output: 
  volker::html_report
---
```

Then, you can generate combined outputs using the report-functions.
One advantage of the report-functions is that plots are automatically 
scaled to fit the page.

# A single categorical variable

```{r}
report_counts(data, sd_gender)
```

# A cross table

```{r}
data %>% 
  filter(sd_gender != "divers") %>% 
  report_counts(adopter, sd_gender, prop="rows", title="Innovator")
```


# Group comparisons of an automaticaly calculated index
```{r}
data %>% 
  filter(sd_gender != "divers") %>% 
  report_metrics(starts_with("cg_adoption_"), sd_gender)

```

# Mix in your own content

If you want to add content before the outputs, 
set the title parameter to `FALSE` and add your 
own title.

A good place for methodological details is a tabsheet 
next to the "Plot" and the "Table" buttons. You can add a tab
by setting the close-parameter to `FALSE` and adding a new header
on the fifth level (5 x # followed by the tab name). Close your new tabsheet with
`#### {-}` (4 x #). See the example Markdown behind this vignette.

### Adoption types

```{r}
data %>% 
  filter(sd_gender != "divers") %>% 
  report_counts(adopter, sd_gender, prop="rows", title=F, close=F)
```


##### Method
Basis: Only male and female respondents.

#### {-}




