
---
title: "Scales and index calculation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Scales and index calculation}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", echo = TRUE)

library(dplyr)
library(ggplot2)
library(volker)
theme_set(theme_bw())

data <- volker::chatgpt

```

```{css, echo=FALSE}
table {margin-left:0 !important;}
h4 {margin-left:0 !important;}
h5 {font-size:100% !important; color: #444 !important;}
```


# Scales

You can calculate mean indexes from a bunch of items using `add_index()`. 
A new column is created with the average value of all selected columns
for each case. 

Reliability and number of items are calculated with `psych::alpha()`
and stored as column attribute named "psych.alpha". The reliability values 
are printed by `tab_metrics()`, see the items and alpha values in the following output.

## Add a single index
```{r}

data %>%
  add_index(
    starts_with("cg_adoption_advantage"),
    newcol = "idx_advantage"
  ) %>%
  report_metrics(idx_advantage)

  
```


## Compare the index values by group

Note: If you don't name the index column explicitly,
it is derived from the common prefix of all selected items.

```{r}
data %>%
  add_index(starts_with("cg_adoption_advantage")) %>%
  report_metrics(idx_cg_adoption_advantage_0, adopter)
```

## Add multiple indizes
```{r}
data %>%
  add_index(starts_with("cg_adoption_")) %>%
  add_index(starts_with("cg_adoption_advantage")) %>%
  add_index(starts_with("cg_adoption_fearofuse")) %>%
  add_index(starts_with("cg_adoption_social")) %>%
  
  report_metrics(starts_with("idx_cg_adoption"))
```

