
---
title: "Table variations"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Table variations}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", echo = TRUE)

library(tidyverse)
library(volker)
theme_set(theme_bw())

data <- volker::chatgpt


# Recode -9 to NA
data <- prepare(data)

```

```{css, echo=FALSE}
table {margin-left:0 !important;}
```

## Frequencies of categorical variables

### 1. One variable: Frequency table of gender
```{r}
tab_counts(data, sd_geschlecht)
```

### 2. Two variables: Cross table of innovator type by gender

```{r}
tab_counts(data, in_adoption, sd_geschlecht)
```


### 3. Multiple items: Frequency table of adoption factors
```{r}
tab_counts(data, starts_with("cg_adoption_"))
```


## Distributions of metric variables

### 1. Distribution table for one metric variable: Age
```{r}
tab_metrics(data, sd_alter)
```

### 2. Group comparison of a metric variable: Age by gender

```{r}
tab_metrics(data, sd_alter, sd_geschlecht)
```

### 3. Distribution table for multiple metric items: Adoption factors
```{r}
tab_metrics(data, starts_with("cg_adoption_"))
```


### 4. Compare means of multiple items: Adoption factors by gender
```{r}
tab_metrics(data, starts_with("cg_adoption_"), sd_geschlecht)
```

## Correlations

*Still experimental*  

### Correlation of items: Adoption factors  

```{r}
tab_metrics_items_cor(data, starts_with("cg_adoption_adv"))
```

### Correlation between different item groups: Adoption factors and usage

```{r}
tab_metrics_items_cor(data, starts_with("cg_adoption_adv"), starts_with("cg_nutzen"))
```


# Scales

You can calculate mean indexes from a bunch of items using `add_idx()`. 
A new column is created with the average value of all selected columns
for each case. 

Reliability and number of items are calculated with `psych::alpha()`
and stored as column attribute named "psych.alpha". The reliability values 
are printed by `tab_metrics()`.

**Add a single index**
```{r}
data %>%
  add_idx(starts_with("cg_adoption_")) %>%
  tab_metrics(idx_cg_adoption)
```

**Compare the index values by group**
```{r}
data %>%
  add_idx(starts_with("cg_adoption_")) %>%
  tab_metrics(idx_cg_adoption, in_adoption)
```

**Add multiple indizes and summarize them**
```{r}
data %>%
  add_idx(starts_with("cg_adoption_")) %>%
  add_idx(starts_with("cg_adoption_advantage")) %>%
  add_idx(starts_with("cg_adoption_fearofuse")) %>%
  add_idx(starts_with("cg_adoption_social")) %>%
  tab_metrics(starts_with("idx_cg_adoption"))
```


# Set custom item labels

Item labels are stored in the comment attribute of an item variable. 
You can set custom or new labels with `labs_apply()` by providing a tibble 
with item names in the first column
and item labels in the second column.

```{r}
newlabels <- tribble(
  ~item_name, ~item_label,
  "cg_adoption_advantage_01", "Allgemeine Vorteile",
  "cg_adoption_advantage_02", "Finanzielle Vorteile",
  "cg_adoption_advantage_03", "Vorteile bei der Arbeit",
  "cg_adoption_advantage_04", "Macht mehr Spaß"
)

data %>%
  labs_apply(newlabels) %>%
  tab_metrics(starts_with("cg_adoption_advantage_"))
```


You can remove all labels with `labs_clear()` to get a plain dataset.

```{r}
data %>%
  labs_clear(everything()) %>%
  tab_counts(starts_with("cg_adoption_advantage_"))
```

