
---
title: "Table variations"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Table variations}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", echo = TRUE)

library(tidyverse)
library(volker)
theme_set(theme_bw())

data <- volker::chatgpt


# Recode -9 to NA
data <- prepare(data)

# Add label to sd_alter
data <- set_item_labels(data, tibble("sd_alter", "Alter"))
```

## Frequencies of categorical variables

### 1. One variable: Frequency table of gender
```{r results='asis'}

tab_counts(data, sd_geschlecht)

```

### 2. Two variables: Cross table of innovator type by gender

```{r results='asis'}
tab_counts(data, in_adoption, sd_geschlecht, missings = T)
```


### 3. Multiple items: Frequency table of adoption factors
```{r results='asis'}
tab_counts(data, starts_with("cg_adoption_"), missings = F)
```


## Distributions of metric variables

### 1. Distribution table for one metric variable: Age
```{r results='asis'}
tab_metrics(data, sd_alter)
```

### 2. Group comparison of a metric variable: Age by gender

```{r results='asis'}
tab_metrics(data, sd_alter, sd_geschlecht)
```

### 3. Distribution table for multiple metric items: Adoption factors
```{r results='asis'}
tab_metrics(data, starts_with("cg_adoption_"))
```


### 4. Compare means of multiple items: Adoption factors by gender
```{r results='asis'}
tab_metrics(data, starts_with("cg_adoption_"), sd_geschlecht)
```

## Correlations

*Still experimental*
### Correlation of items: Adoption factors
```{r results='asis'}
tab_metrics_items_cor(data, starts_with("cg_adoption_adv"))

tab_metrics_items_cor(data, starts_with("cg_adoption_adv"), starts_with("cg_nutzen"))
```


# Scales

You can calculate mean indizes from a bunch of items using `add_idx()`. 
A new column is created with the average value of all selected columns
for each case. 

Reliability and number of items are calculated with `psych::alpha()`
and stored as column attribute named "psych.alpha". The reliability values 
are printed by `tab_metrics()`.


```{r results='asis'}
# Add a single index
data %>%
  add_idx(starts_with("cg_adoption_")) %>%
  tab_metrics(idx_cg_adoption)

# Compare the index values by group
data %>%
  add_idx(starts_with("cg_adoption_")) %>%
  tab_metrics(idx_cg_adoption, in_adoption)
```


```{r results='asis'}

# Add multiple indizes and summarize them
data %>%
  add_idx(starts_with("cg_adoption_")) %>%
  add_idx(starts_with("cg_adoption_advantage")) %>%
  add_idx(starts_with("cg_adoption_fearofuse")) %>%
  add_idx(starts_with("cg_adoption_social")) %>%
  tab_metrics(starts_with("idx_cg_adoption"))

```


# Set custom item labels

Item labels are stored in the comment attribute of an item variable. 
When printing item tables, the labels are used. You can set custom or 
new labels by providing a tibble with item names in the first column
and item labels in the second.

```{r results='asis'}
newlabels <- tribble(
  ~item_name, ~item_label,
  "cg_adoption_advantage_01", "Allgemeine Vorteile",
  "cg_adoption_advantage_02", "Finanzielle Vorteile",
  "cg_adoption_advantage_03", "Vorteile bei der Arbeit",
  "cg_adoption_advantage_04", "Macht mehr Spaß"
)

data %>%
  set_item_labels(newlabels) %>%
  tab_metrics(starts_with("cg_adoption_advantage_"))
```


You can remove all labels to get a plain dataset

```{r results='asis'}
data %>%
  labs_clear(everything()) %>%
  tab_counts(starts_with("cg_adoption_advantage_"))
```

