
---
title: "Table variations"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Table variations}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", echo = TRUE)

library(dplyr)
library(volker)

data <- volker::chatgpt

```

```{css, echo=FALSE}
table {margin-left:0 !important;}
```

## Frequencies of categorical variables

### 1. One variable: Frequency table of gender
```{r}
tab_counts(data, sd_gender)
```

### 2. Two variables: Cross table of innovator type by gender

```{r}
tab_counts(data, adopter, sd_gender)
```


### 3. Multiple items: Frequency table of adoption factors
```{r}
tab_counts(data, starts_with("cg_adoption_"))
```


## Distributions of metric variables

### 1. Distribution table for one metric variable: Age
```{r}
tab_metrics(data, sd_age)
```

### 2. Group comparison of a metric variable: Age by gender

```{r}
tab_metrics(data, sd_age, sd_gender)
```

### 3. Distribution table for multiple metric items: Adoption factors
```{r}
tab_metrics(data, starts_with("cg_adoption_"))
```


### 4. Compare means of multiple items: Adoption factors by gender
```{r}
tab_metrics(data, starts_with("cg_adoption_"), sd_gender)
```

## Correlations

### Correlation of items: Adoption factors  

```{r}
tab_metrics_items_cor(data, starts_with("cg_adoption_adv"), starts_with("cg_adoption_adv"), labels=F)
```

### Correlation between different item groups: Adoption factors and usage

```{r}
tab_metrics_items_cor(data, starts_with("cg_adoption_adv"), starts_with("use_"), digits=2)
```

