
---
title: "Table variations"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Table variations}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", echo = TRUE)

library(dplyr)
library(volker)

data <- volker::chatgpt

```

```{css, echo=FALSE}
table {margin-left:0 !important;}
```

## Frequencies of categorical variables

### 1. One variable: Frequency table of gender

```{r}
tab_counts(data, sd_gender)
```

### 2. Two variables: Cross table of innovator type by gender

```{r}
tab_counts(data, adopter, sd_gender)
```

### 3. Two variables: One categorical and one metric [and... one categorical one categorical correlated]

```{r}
# Redirected to tab_metrics
tab_counts(data, adopter, sd_age, metric = T)
# equals ...
tab_metrics(data, sd_age, adopter)

# TODO: implement npmi confidence intervals for cor 
# Implement method param = "cor" vs. "grouped" instead of cor = T ? 
tab_counts(data, adopter, use_work, cor = T)

```

### 4. Multiple items: Frequency table of adoption factors
```{r}
tab_counts(data, starts_with("cg_adoption_"))
```

### 5. Multiple grouped items: Frequency table of adoption factors grouped by gender
```{r}
tab_counts(data, starts_with("cg_adoption_"), sd_gender, 
           category = c("agree", "strongly agree"))
```

### 6. Multiple categorical items and one metric variable [... and categorical items and one categorical]
```{r}

# if metric redirect to tab_metrics
# Group comparison per item not implemented, would be correlated here,
# hence cor param questionable? 

# by now... 
tab_counts(data, starts_with("use_"), sd_age, metric = T)
# equals.. 
tab_metrics(data, starts_with("use_"), sd_age, metric = T)

# TODO: implement nmpi calculation for categorical 
data |>
 tidyr::pivot_longer(starts_with("use_")) |>
 tab_metrics(value, name)

tab_counts(data, starts_with("use_"), adopter)

```


## Distributions of metric variables

### 1. Distribution table for one metric variable: Age
```{r}
tab_metrics(data, sd_age)
```

### 2. Group comparison of a metric variable: Age by gender

```{r}
tab_metrics(data, sd_age, sd_gender)
```

### 3. Distribution table for multiple metric items: Adoption factors
```{r}
tab_metrics(data, starts_with("cg_adoption_"))
```


### 4. Compare means of multiple items: Adoption factors by gender
```{r}
tab_metrics(data, starts_with("cg_adoption_"), sd_gender)
```

## Correlations

### Correlation of two single variables

```{r}
tab_metrics(data, use_private, use_work, metric=T, labels=F)
```

### Correlation of items with one single variable

```{r}
tab_metrics(data, starts_with("cg_adoption_adv"), sd_age, metric=T, digits=2)
```


### Correlation of items

```{r}
tab_metrics(data, starts_with("cg_adoption_adv"), metric=T, starts_with("cg_adoption_adv"), labels=F)
```

### Correlation of different item groups

```{r}
tab_metrics(data, starts_with("cg_adoption_adv"), starts_with("use_"), metric=T, digits=2)
```


