---
title: "Table variations"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Table variations}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", echo = TRUE)

library(dplyr)
library(volker)

data <- volker::chatgpt

```

```{css, echo=FALSE}
table {margin-left:0 !important;}
```

| \# | function                        | implemented | col scale | col count | cross scale | cross count |
|----|---------------------------------|-------------|-----------|----------|--------------|-------------|
| 1  | tab_counts_one                  |             | counts    | one      |              |             |
| 2  | tab_counts_one_grouped          |             | counts    | one      | counts       | one         |
| 3  | tab_counts_one_cor              |             | counts    | one      | metric       | one         |
| 4  | tab_counts_items                |             | counts    | multiple |              |             |
| 5  | tab_counts_items_grouped        |             | counts    | multiple | counts       | one         |
| 6  | tab_counts_items_grouped_items  |             | counts    | multiple | counts       | multiple    |
| 7  | tab_counts_items_cor            |             | counts    | multiple | metric       | one         |
| 8  | tab_counts_items_cor_items      | not yet     | counts    | multiple | metric       | multiple    |
| 9  | tab_metrics_one                 |             | metric    | one      |              |             |
| 10 | tab_metrics_one_grouped         |             | metric    | one      | counts       | one         |
| 11 | tab_metrics_one_cor             |             | metric    | one      | metric       | one         |
| 12 | tab_metrics_items               |             | metric    | multiple |              |             |
| 13 | tab_metrics_items_grouped       |             | metric    | multiple | counts       | one         |
| 14 | tab_metrics_items_grouped_items | not yet     | metric    | multiple | counts       | multiple    |
| 15 | tab_metrics_items_cor           |             | metric    | multiple | metric       | one         |
| 16 | tab_metrics_items_cor_items     |             | metric    | multiple | metric       | multiple    |

## Frequencies of categorical variables

### 1. One variable: Frequency table of gender

```{r}
tab_counts(data, sd_gender)
```

### 2. Two variables: Cross table of innovator type by gender

```{r}
tab_counts(data, adopter, sd_gender, prop="cols")
```

### 3. Two variables: One categorical and one metric variable split at the median

```{r}
tab_counts(data, adopter, sd_age, metric=T)
```

### 4. Multiple items: Frequency table of adoption factors

```{r}
tab_counts(data, starts_with("cg_adoption_"))
```

### 5. Multiple grouped items: Frequency table of adoption factors grouped by gender

```{r}
tab_counts(
  data, starts_with("cg_adoption_"), sd_gender, 
  category = c("agree", "strongly agree")
)
```

### 6. Correlation of categorical items with categorical items

```{r}
tab_counts(data, starts_with("cg_adoption_adv"), starts_with("use_"))
```


### 7. Multiple categorical items and one metric variable

```{r}

tab_counts(
  data, starts_with("cg_adoption_"), sd_age, metric = TRUE,
  category = c("agree", "strongly agree")
)

```

### 8. Correlation of categorical items with metric items

```{r}
# TODO
#tab_counts(data, starts_with("cg_adoption_adv"), starts_with("cg_adoption_adv"), metric = TRUE)
```

## Distributions of metric variables

### 9. Distribution table for one metric variable: Age

```{r}

tab_metrics(data, sd_age)
```

### 10. Group comparison of a metric variable: Age by gender

```{r}
tab_metrics(data, sd_age, sd_gender)
```

### 11. Correlation of two single variables

```{r}
tab_metrics(data, use_private, use_work, metric=T, labels=F)
```

### 12. Distribution table for multiple metric items: Adoption factors

```{r}
tab_metrics(data, starts_with("cg_adoption_"))
```

### 13. Compare means of multiple items: Adoption factors by gender

```{r}
tab_metrics(data, starts_with("cg_adoption_"), sd_gender)
```

### 14. Correlation of metric items with categorical items

```{r}
# TODO
# tab_metrics(data, starts_with("cg_adoption_adv"), starts_with("use_"))
```

### 15. Correlation of items with one single variable

```{r}
tab_metrics(data, starts_with("cg_adoption_adv"), sd_age, metric=T)
```

### 16. Correlation of metric items with metric items

```{r}

tab_metrics(
  data, 
  starts_with("cg_adoption_adv"), 
  starts_with("use_"),
  metric = TRUE, ci = T
)

```

