---
title: "Create example plots and tables"
output: rmarkdown::html_vignette
editor_options: 
  chunk_output_type: console
---

```{r include=FALSE}

knitr::opts_knit$set(root.dir = "../..")
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", echo=FALSE, fig.width = 7)

library(tidyverse)
library(volker)
theme_set(theme_bw())

data <- volker::chatgpt
data <- prepare(data)

# Simplify labels for examples
data <- data |> 
  labs_store() |> 
  mutate(adopter = case_when(
    adopter == "I try new offers immediately" ~ "I try quickly",
    adopter == "I try new offers rather quickly" ~ "I try quickly",
    adopter == "I wait until offers establish themselves" ~ "I tend to wait",
    adopter == "I only use new offers when I have no other choice" ~ "I tend to wait"
  )) |> 
  labs_restore()

data <- data %>%
  labs_apply(tribble(
    ~item_name, ~item_label,
    "cg_adoption_advantage_01", "Benefits: General", 
    "cg_adoption_advantage_02", "Benefits: Financial",
    "cg_adoption_advantage_03", "Benefits: Workplace",
    "cg_adoption_advantage_04", "Benefits: Joy"
  ))
```

## 1. One variable

### Metric: Age
```{r}

data %>%
  tab_metrics(sd_age)

data %>%
  plot_metrics(sd_age)

ggsave("man/figures/plot_metrics_one.png", width=300,height=200, units="px", dpi=96)

```


### Categorical: Adoption
```{r}

data %>% 
  tab_counts(adopter)

data %>% 
  plot_counts(adopter)

ggsave("man/figures/plot_counts_one.png", width=300,height=200, units="px", dpi=96)

```

## 2. Two variables (one being categorical)

### Group comparison: Age by gender

```{r results='asis'}

data |> 
  tab_metrics(sd_age, sd_gender)

data %>% 
  filter(sd_gender != "diverse") %>% 
  plot_metrics(sd_age, sd_gender)

ggsave("man/figures/plot_metrics_one_grouped.png", width=300,height=200, units="px", dpi=96, scale = 1)
```


### Cross table: Innovator type by gender

```{r}

data %>% 
  tab_counts(adopter, sd_gender)

data %>% 
  select(sd_gender, adopter) |> 
  filter(sd_gender != "diverse") %>% 
  filter(adopter %in% c("I tend to wait", "I try quickly")) %>% 
  plot_counts(adopter, sd_gender, prop="rows", ordered = 1) +
  theme(legend.position = "bottom")

ggsave("man/figures/plot_counts_one_grouped.png", width=300,height=200, units="px", dpi=96, scale = 1)
```


## 2. Multiple items

### Adoption factors as metric variables
```{r}

data %>% 
  tab_metrics(starts_with("cg_adoption_advantage_"))

data |> 
  select(starts_with("cg_adoption_advantage_")) |> 
  labs_apply(
    tribble(
      ~value_name, ~value_label,
      "1" , "not at all",
      "2", "",
      "3", "",
      "4", "",
      "5" , "fully applies"
    ),
    cols = starts_with("cg_adoption_advantage_")
  )  |>
  plot_metrics_items(starts_with("cg_adoption_advantage_")) 

ggsave("man/figures/plot_metrics_items.png", width=600,height=400, units="px", dpi=96, scale = 0.5)
```


### Adoption factors as frequencies
```{r}

# TODO: better recode 1+2 and 4+5
data %>% 
  filter(
    cg_adoption_advantage_01 %in% c(1,3,5),
    cg_adoption_advantage_02 %in% c(1,3,5),
    cg_adoption_advantage_03 %in% c(1,3,5),
    cg_adoption_advantage_04  %in% c(1,3,5)
    
  ) %>% 
  tab_counts(starts_with("cg_adoption_advantage_"))

data %>% 
  plot_counts_items(starts_with("cg_adoption_advantage_")) +
  theme(legend.position = "none")

ggsave("man/figures/plot_counts_items.png", width=600,height=400, units="px", dpi=96, scale = 0.5)
```


## 4. Multiple metric variables

### Compare means of multiple items: Adoption factors by gender
```{r results='asis'}

data %>% 
  tab_metrics(
    starts_with("cg_adoption_advantage"), 
    sd_gender
  )

```

### Correlation of items: Adoption factors by adoption factors
```{r results='asis'}

data %>% 
  tab_metrics_items_cor(starts_with("cg_adoption_advantage"))

```
